Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup

### 2013-08-02 snapshot_system/failover.tex
normalized axis label and legend fonts, switched to sans-serif for plots

\begin{figure}[htbp]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={VO FSB links},
		xlabel={Number of VMs},
		ylabel={\small Avg. Num. VMs sharing FSB},
                cycle list name=mline,
                xmin=0,
                ymin=0,
                xmax=106,
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
		legend pos=north west
		]
                \addplot table[x=VMs,y=FSBLinks] {figures/vo_fsb_links_105.txt};
		\addplot table[x=VMs,y=cdslinks] {figures/cds_links_105.txt};
                \legend{VO, PDS in VC};
		\end{axis}
	\end{tikzpicture}
  \caption{Measured Average number of VMs sharing a 64MB FSB with global dedup (VO), and in a 2\% PDS for VC.}
  \label{fig:fsb-links}
\end{figure}

\begin{figure}[htbp]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={VO VM links},
		xlabel={Number of VMs},
		ylabel={\small Avg. Num. FSBs used by VM},
                xmin=0,
                ymin=0,
                xmax=106,
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
		legend pos=south west
		]
                \addplot[blue,mark=none] table[x=VMs,y=No] {figures/vo_vm_links_105.txt};
                \addplot[red,dotted,mark=none] table[x=VMs,y expr=\thisrow{N1}+\thisrow{N2}] {figures/vc_vm_links_105.txt};
                \addplot[red,densely dashed,mark=none] table[x=VMs,y=N2] {figures/vc_vm_links_105.txt};
                \addplot[red,dashdotted] table[x=VMs,y=N1] {figures/vc_vm_links_105.txt};
                \legend{$N_o$, $N_1+N_2$, $N_2$, $N_1$};
		\end{axis}
	\end{tikzpicture}
  \caption{Measured Average number of 64MB FSBs used by a single VM. For VC both the number of PDS and Non-PDS FSBs used are shown.}
  \label{fig:vm-links}
\end{figure}
The snapshot availability of is a VM is the likelyhood that
there is no  data loss for all its file blocks.
With replication degree $r$, the likelyhood of
a file block block is the probability that  
all of its replicas appear in $d$ failed machines. 
Namely, $\binom{d}{r}/ \binom{p}{r}$. This can be seen in Figure~\ref{fig:fsb-availability} for a 100 machine cluster for 3 different replication factors.

@@

}
\begin{figure}[htbp]
  \centering
    \begin{tikzpicture}
            \begin{axis}[
            %title={FSB Availability},
            cycle list name=mline,
            xlabel={Number of Machines Failed},
            ylabel={\small Availability of Single FSB (\%)},
            extra y ticks={99.9}, %to add extra ticks
            mark options=solid,
            legend pos=south west,
            %legend columns=2,
            %legend style={
            %    at={(0.5,-0.2)},
            %anchor=north}
            ]
            \addplot table[x=NodesFailed,y=Availability5] {figures/fsb_availability.txt};
            \addplot table[x=NodesFailed,y=Availability4] {figures/fsb_availability.txt};
            \addplot table[x=NodesFailed,y=Availability3] {figures/fsb_availability.txt};
            \legend{$R=5$,$R=4$,$R=3$};
            \end{axis}
    \end{tikzpicture}
    \caption{Availability of Individual FSBs in 100 Machine Cluster with different replication factors.}
  \label{fig:fsb-availability}
\end{figure}

>>>>

\begin{figure}[htbp]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={VO FSB links},
		xlabel={Number of VMs},
		ylabel={Avg. Num. VMs sharing FSB},
                cycle list name=mline,
                xmin=0,
                ymin=0,
                xmax=106,
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
		legend pos=north west
		]
                \addplot table[x=VMs,y=FSBLinks] {figures/vo_fsb_links_105.txt};
		\addplot table[x=VMs,y=cdslinks] {figures/cds_links_105.txt};
                \legend{VO, PDS in VC};
		\end{axis}
	\end{tikzpicture}
  \caption{Measured Average number of VMs sharing a 64MB FSB with global dedup (VO), and in a 2\% PDS for VC.}
  \label{fig:fsb-links}
\end{figure}

\begin{figure}[htbp]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={VO VM links},
		xlabel={Number of VMs},
		ylabel={Avg. Num. FSBs used by VM},
                xmin=0,
                ymin=0,
                xmax=106,
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
		legend pos=south west
		]
                \addplot[blue,mark=none] table[x=VMs,y=No] {figures/vo_vm_links_105.txt};
                \addplot[red,dotted,mark=none] table[x=VMs,y expr=\thisrow{N1}+\thisrow{N2}] {figures/vc_vm_links_105.txt};
                \addplot[red,densely dashed,mark=none] table[x=VMs,y=N2] {figures/vc_vm_links_105.txt};
                \addplot[red,dashdotted] table[x=VMs,y=N1] {figures/vc_vm_links_105.txt};
                \legend{$N_o$, $N_1+N_2$, $N_2$, $N_1$};
		\end{axis}
	\end{tikzpicture}
  \caption{Measured Average number of 64MB FSBs used by a single VM. For VC both the number of PDS and Non-PDS FSBs used are shown.}
  \label{fig:vm-links}
\end{figure}
The snapshot availability of is a VM is the likelyhood that
there is no  data loss for all its file blocks.
With replication degree $r$, the likelyhood of
a file block block is the probability that  
all of its replicas appear in $d$ failed machines. 
Namely, $\binom{d}{r}/ \binom{p}{r}$. This can be seen in Figure~\ref{fig:fsb-availability} for a 100 machine cluster for 3 different replication factors.

@@

}
\begin{figure}[htbp]
  \centering
    \begin{tikzpicture}
            \begin{axis}[
            %title={FSB Availability},
            cycle list name=mline,
            xlabel={Number of Machines Failed},
            ylabel={Availability of Single FSB (\%)},
            extra y ticks={99.9}, %to add extra ticks
            mark options=solid,
            legend pos=south west,
            %legend columns=2,
            %legend style={
            %    at={(0.5,-0.2)},
            %anchor=north}
            ]
            \addplot table[x=NodesFailed,y=Availability5] {figures/fsb_availability.txt};
            \addplot table[x=NodesFailed,y=Availability4] {figures/fsb_availability.txt};
            \addplot table[x=NodesFailed,y=Availability3] {figures/fsb_availability.txt};
            \legend{$R=5$,$R=4$,$R=3$};
            \end{axis}
    \end{tikzpicture}
    \caption{Availability of Individual FSBs in 100 Machine Cluster with different replication factors.}
  \label{fig:fsb-availability}
\end{figure}
